\section{Problem formulation}

This is a supervised multi-class classification problem. For each targetted
ambiguous word $w$, we train an classifier $h_w: X \rightarrow L$, where X is
the feature space (context representation), and the label space L is the list of
word definitions for word w given by WordNet~\cite{wordnet}.

\textbf{Data Preprocessing}.

We plan to use SemCor Corpus~\cite{semcor} as our data set. SemCor Corpus is a
corpus where each word is tagged with a sense provided by WordNet~\cite{wordnet}.

\begin{enumerate}
  \item Tokenization: transform the sentense strings into list of tokens
    (usually words).
  \item Part-of-Speech tagging: e.g. ``the/DT bar/NN was/VBD crowded/JJ'', where
    DT stands for Determiners, NN stands for Noun, etc.
  \item Lemmatization: e.g. $plays \rightarrow play$, $was \rightarrow be$.
  \item Feature extraction: select some features to represent the context.
\end{enumerate}

Feature extraction (context representation): 
(1) Colocation~\cite{colocation}. The preceding and succeeding words and their
Part-of-Speech tags.  (2) Bag-of-words~\cite{bagofwords}. Ignore positional
information. Assume that there is a fixed set of vocabulary that represent a
relevant topic, transform the appearance of those words as a bit vector.

\textbf{Construct training set for each target word}.\\
Let W be the set of English words that we want to do sense disambiguation. For
each $w \in W$, we need to extract a training set $X_w$ from the SemCor Corpus
as follow: 
\begin{enumerate}
  \item Draw a set of sentences $S_w$ from SemCor Corpus, where each 
$s \in S_w$ contains w. 
  \item Convert each sentence $s \in S_w$ to a feature vector x, and the sense
    label y. The set of all (x,y) pairs is our training set $X_w$.
\end{enumerate}

